\newpage
%\section{References}
%\label{sec:References}

\begin{thebibliography}{9}
\bibitem{SORA}
S.A. Garcia Morelos, F.Brooks, S.Oliver, A.Walker, K.D. Portillo, R.B. Masek, D.Mroczek, D.Pena, J.Juarez, A.Cruz, D. Henandez, S.George, D. Pattison, A.L.Renshaw. \textit{Scientific Report for the UH Team.} SORA 2017 Mission Webpage. \url{http://laspace.lsu.edu/hasp/groups/Payload.php?py=2017&pn=10}.

\bibitem{silicon_sensor}
  MiniPIX - Miniaturized Portable USB Photon Counting Camera. (n.d.). Retrieved February 02, 2017, from \url{http://advacam.com/camera/minipix}.

\bibitem{LSU}
  Christner, B., Alleman, M., Bryan, N., Burke, S., Guzik, T.G., Granger, D., King, G. (2013) \textit{LSU HASP2013 PDF. Baton Rouge: Louisiana Space Consortium}.

 \bibitem{Solidworks}
   SolidWorks 3D CAD software \url{http://www.solidworks.com/}.
  
 \bibitem{COMSOL}
   COMSOL Multiphysics Simulation software \url{http://www.comsol.com}.

\bibitem{Extremophiles}
  Extremophiles \href{http://www.nytimes.com/2013/02/07/science/living-bacteria-found-deep-under-antarctic-ice-scientists-say.html}{http://www.nytimes.com/2013/02/07/science/living-bacteria-found-deep-\\under-antarctic-ice-scientists-say.html}.

\bibitem{canales}
 Canales D. C. and Ehteshami A., \textit{An attempt to sample atmospheric bacteria}, Houston, TX, 2015, January 11.

\bibitem{bexus}
Urbar, J., Scheirich, J., Jakubek, J., 2011. Medipix/Timepix cosmic ray tracking on BEXUS stratospheric balloonflights. Nucl. Instrum. Methods A 633, S206-209.
	
\bibitem{uv_irradiance}
  Calculating the UV Index. (2016, October 14). Retrieved June 03, 2017, from \url{https://www.epa.gov/sunsafety/calculating-uv-index-0}.

\bibitem{UVonDNA}
  Cockell CS, Horneck G., \textit{The history of the UV radiation climate of the earth--theoretical and space-based observations.}, Photochem Photobiol. 73(4):447-51 (2001).

\bibitem{cleanbox}
Clean box material \url{https://www.mcmaster.com/\#uhmw-polyethylene/=1aijn1p}.

\bibitem{valve}
Valve data sheet \url{http://www.generant.com/Literature/Series\%20VRV\%20Product\%20Literature.pdf}.

\bibitem{advacam}
  ADVACAM at \url{advacam.com}.

\bibitem{medipix}
  Medipix collaboration at \url{https://medipix.web.cern.ch/}.

\bibitem{JIC 139} 
  ELECTRO OPTICAL COMPONENTS, \textit{JIC 139}, Retrieved October, 17, 2017, from \url{inc.com/UV_detectors_silicon_carbide_photodiodes.html}.

\bibitem{Thor Labs} 
  Thor Labs, \textit{Unmounted UV Fused Silica Reflective ND Filters}. Retrieved August, 18, 2017, from \url{https://www.thorlabs.com/newgrouppage9.cfm?objectgroup_id=6106}.

\bibitem{RTL}
  RTL Genomics at \url{http://rtlgenomics.com/}.

\bibitem{lemon}
PCR Method at \url{http://www.journal-of-hepatology.eu/article/S0168-8278(17)32278-X/fulltext}.
	
\bibitem{illumina}
	Illumina, Inc. San Diego, California at \url{https://www.illumina.com/}

\bibitem{Microbial rRNA sequencing}
Microbial rRNA sequencing \url{http://pubs.rsc.org/En/content/articlehtml/2017/em/c6em00413j}.
  
\bibitem{stuartthesis} 22
  George, S., \textit{Dosimetric Applications of Hybrid Pixel Detectors}, University of Wollongong, Australia, 2015.

\bibitem{mpdatasheet}
  ADVACAM, \textit{MINIPIX Version 1.0 Datasheet}, Retrieved from \url{http://www.widepix.cz/files/datasheets/MiniPIX\%20v1.0\%20Datasheet.pdf}.

  \bibitem{numpy} 
  Numpy scientific computing library at \url{http://www.numpy.org/}.

\bibitem{stuartalgo}
	Reprinted from \textit{Dosimetric Applications of Hybrid Pixel Detectors} by Stuart George, 2015, Mixed Field Measurements and Cluster Formation with Timepix,52.

 \bibitem{regener}
 Regener E. \& Pfotzer G., \textit{Vertical Intensity of Cosmic Rays by Threefold Coincidences in the Stratosphere.}, Nature 136, 718-719, (1935). 

\bibitem{spaceballoonnetwork}
Space weather archives \url{http://spaceweather.com/archive.php?view=1&day=12&month=10&year=2016}.

\bibitem{dyastima}
  Paschalis, P. et al., \textit{Geant4 software application for the simulation of cosmic ray showers in the Earth? atmosphere. New Astronomy} {\bf 33} (2014):26.

\bibitem{geant4}
  Geant4 simulation toolkit at \url{http://geant4.cern.ch/}.


%\bibitem{mpjakubek}
%  Jan Jakubek, \textit{Precise energy calibration of pixel detector working in time-over-threshold mode} Institute of Experimental and Applied Physics, Czech Technical University in Prague, Czech Republic, 2011.
  

    


%\bibitem{magnetictool}
%  United States National Oceanic and Atmospheric Administration, \textit{Magnetic Field Calculators} [Data sets], Retrieved from \url{https://www.ngdc.noaa.gov/geomag-web/#igrfwmm}.

%\bibitem{gorman}
%	Gorman, J. (2013, February 06). \textit{Scientists Find Life in the Cold and Dark Under Antarctic Ice.} Retrieved September 15, 2016, from Scientists Find Life in the Cold and Dark Under Antarctic Ice.
	
 
 
%\bibitem{pumpsource}
%  \url{http://www.knfusa.com/?type=5600&amp;file=2079}.


%\bibitem{Horneck}
%  Horneck, G. 1993. The Biostack concept and its application in space and at accelerators: studies in Bacillus subtilis spores, p. 99-115. In C. E. Swenberg, G. Horneck, and E. G. Stassinopoulos (ed.), \textit{Biological effects and physics of solar and galactic cosmic radiation}[PDF], part A. Plenum Press, New York, NY. accessed 10/24/16  

%\bibitem{Horneck} 
%  Horneck, G. 2007. \textit{Space radiation biology}[PDF], p. 243-273. In E. Brinckmann (ed.), Biology in space and life on Earth. Wiley-VCH, Weinheim, Germany. Accessed 10/26/16

%\bibitem{Horneck}
%  Horneck, G., C. Baumstark-Khan, and G. Reitz. 2002. \textit{ Space microbiology: effects of ionizing radiation on microorganisms in space}[PDF], p. 2988-2996. In G. Bitton (ed.), The encyclopedia of environmental microbiology. John Wiley \& Sons, New York, NY. Accessed 10/30/16

%\bibitem{Horneck}
%  Horneck, G., C. Baumstark-Khan, and R. Facius. 2006. \textit{Radiation biology}[PDF], p. 292-335. In G. Cl?ment and K. Slenzka (ed.), Fundamentals of space biology. Kluwer Academic Publishers/Springer, Dordrecht, The Netherlands. accessed 11/4/16

%\bibitem{Kiefer}
%Kiefer, J., K. Schenk-Meuser, and M. Kost. 1996. \textit{Radiation biology}[PDF], p. 300-367. In D. Moore, P. Bie, and H. Oser (ed.), Biological and medical research in space. Springer, Berlin, Germany. accessed 11/9/16
 
	

\bibitem{SamURD}
	Alfonso Garcia Morelos, S. (2016, October 13).
	\textit{A Novel Microbe Trap.}
	Presentation at UH Undergraduate Research Day. \url{http://www.uh.edu/honors/undergraduate-research/}
	
	
%\bibitem{StevenURD}

%\bibitem{FreEttaWomensConference}

%\bibitem{StevenSchoolPres}

\bibitem{StevenURD}
  Oliver, S. J. (2017, October 12). 
  \textit{Stratospheric Organism and Radiation Analyzer}
  Presentation at UH Undergraduate Research Day. Retrieved October 12, 2017, from \url{http://www.uh.edu/honors/undergraduate-research/events/urday2017/}

\bibitem{StevenSchoolPres}
  Oliver, S. J. (2017, November 4). 
  \textit{STEM Life at UH}
  Presentation at UH Gathering of the Eagles STEM Symposium. \url{https://www.uh.edu/news-events/stories/2016/November/110416EaglesSTEM.php}

\bibitem{Fre}
  Brooks, F. (2017, January 14).
  \textit{Stratospheric Organism and Radiation Analyzer}
  Presentation at Rice University, APS Conferences for Undergraduate Women in Physics (CUiP). \url{http://www.google.com/url?q=http%3A%2F%2Fwww.aps.org%2Fprograms%2Fwomen%2Fworkshops%2Fcuwip.cfm&sa=D&sntz=1&usg=AFQjCNE5pImV-SVrb87CvgAa9RSfeCrYXg}  
  
  \bibitem{SamAPS}
	Alfonso Garcia Morelos, S. (2017, October 20).
	\textit{Stratospheric Organism and Radiation Analyzer}
	Retrieved October 20, 2017, from \textit{Bulletin of the American Physical Society}. \url{https://meetings.aps.org/Meeting/TSF17/Session/E5.3}
	
  
  \bibitem{MIT}
	MIT-Lemelson Award 2018.
	\url{https://lemelson.mit.edu/}
  

\end{thebibliography}